### 2016-09-20 thesis/results/results.tex
tmp commit

>>>>

In this chapter, the relationship between the obesity-associated genetic signatures from previous studies and different cancer types were investigated; new obesity-associated genetic signatures were identified in the data set from \citet{Creighton2012} study; and the presence of common genes or pathways across different cancer types was examined.
